Scattering from compact objects, Regge poles \\ and the Complex Angular Momentum method

### 2019-10-02 rainbowCAM.tex
added some references

We consider the scalar field, with modes that obeys an equation of motion very similar to the axial gravitational wave modes. Accordingly, a similar spectrum for scalar modes can be expected (with no fluid excitation). Whilst these are arguably of less astrophysical interest, they are nonetheless a good model for axial GWs and allow us to make a first step towards a CAM approach for perturbed relativistic stars. We will classify the scalar $\omega$-modes as the axial GW modes have been, we have

>>>>

We consider the massless scalar field which only couples to the body via gravitation. The scalar modes obey an equation of motion very similar to the axial gravitational wave sector. Accordingly, a similar spectrum for scalar modes can be expected (with no fluid excitation). Whilst these are arguably of less astrophysical interest, they are nonetheless a good model for axial GWs and allow us to make a first step towards a CAM approach for perturbed relativistic stars. We will classify the scalar $\omega$-modes as the axial GW modes have been, we have
